\section{Experience}


\begin{twocolentry}{
		August 2024 – Present 
	}
	\textbf{Backend Engineer} \\
	\href{https://nojom.com/}{\textbf{Nojom}} – Remote, Saudi Arabia \\
	\textit{AdTech SaaS | Influencer Marketing Platform}
	\begin{highlights}
		\item Engineered scalable backend infrastructure for marketplace connecting 5,000+ brands and influencers. Integrated \textbf{\textit{MoneyHash payment orchestrator}} processing hundreds of transactions monthly (99.8\% uptime) and deployed comprehensive \textbf{\textit{wallet system}} reducing settlement time from 7 days to 24 hours.
		\item Built \textbf{\textit{AI-powered influencer recommendation engine}} using OpenAI embeddings, improving brand-influencer match rates by 45\% and campaign setup time by 30\%. Optimized database queries and API performance, reducing response time from 60s to 270ms and supporting 10K+ concurrent users.
		\item Implemented \textbf{\textit{AWS Secrets Manager}} with automated rotation via EventBridge/Lambda for SOC 2 compliance. Deployed zero-downtime strategy using PM2 rolling updates, achieving 100\% request completion during deployments.
	\end{highlights}
\end{twocolentry}

\vspace{0.4 cm}

\begin{twocolentry}{
		January 2025 – October 2025
	}
	\textbf{Technical Project Manager} \\
	\href{https://mazad-arab.creteagency.com/}{\textbf{Mzad Arab}} – Remote, Qatar \\
	\textit{E-Commerce | Auction \& Social Marketplace Platform}
	\begin{highlights}
		\item Led end-to-end technical delivery of auction marketplace across Android, iOS, and web, coordinating external teams to launch within 8-month timeline. Managed development roadmap, defined tech stack (Kotlin, Swift, Firebase, PHP, Node.js, React, MySQL), and tracked 100+ feature milestones.
		\item Conducted technical validation and QA of auction systems and social features, identifying and resolving 200+ bugs pre-launch. Established project management infrastructure using ClickUp, supporting distributed team of 12 contributors.
	\end{highlights}
\end{twocolentry}

\vspace{0.4 cm}

\begin{twocolentry}{
		November 2022 – December 2024
	}
	\textbf{Software Engineer} \\
	\href{https://techhive.dev/}{\textbf{Tech Hive}} – Remote, Egypt \\
	\textit{Software House | AI Solutions \& SaaS Development}
	\begin{highlights}
		\item \href{https://appasap.ai}{\textbf{AppAsap}} – Architected AI-powered SaaS platform auto-generating production-ready RESTful APIs, database schemas, and admin dashboards from natural language (70\% development time reduction). Built \textbf{\textit{MCP server}} for Cursor IDE integration, expanding ecosystem reach by 200\%. Automated AWS deployments with Terraform/ArgoCD, reducing infrastructure provisioning from 4 hours to 15 minutes.
		\item \href{https://sal125.smartsway.com}{\textbf{SAL125}} – Developed multilingual life management platform serving 3,000+ users. Integrated OpenAI Assistant API handling 15K+ monthly interactions. Architected scalable AWS infrastructure with ECS/ECR containerization achieving 99.95\% uptime.
		\item \href{https://app.essam.ai}{\textbf{Essam AI}} – Built AI-driven Lean Six Sigma optimization platform. Implemented OpenAI Assistant API for intelligent process analysis and automated Swimlane Diagram generation, reducing process mapping time from 8 hours to 30 minutes.
	\end{highlights}
\end{twocolentry}

